---
title: "Reaction time experiment"
author: "Daniel Lundgaard"
date: "15-09-2022"
output: 
  html_document:
    toc: true
editor_options: 
  markdown: 
    wrap: 80
  chunk_output_type: inline
---

```{r include=FALSE}
knitr::opts_knit$set(root.dir = file.path(getwd()), warning = FALSE) # Setting `knitr` options 
```

## Loading dependencies

```{r message=FALSE}
library(tidyverse)
library(magrittr)
library(lubridate)
```

## Reading in data source

```{r message=FALSE}
data <- read_csv("results.csv")
```

## First look

```{r}
head(data)
```
```{r}
summary <- 
  data %>%
  group_by(type) %>%
  summarise(samples = n(), mean=round(mean(score), digits=2), median=round(median(score), digits=2), sd=round(sd(score), 2))
summary
```

## Applying readable label names for test conditions and setting order

```{r message=FALSE}
type_id <- new.env()
type_id[["reaction_visual"]] <- "Visual reaction"
type_id[["reaction_auditory"]] <- "Auditory reaction"
type_id[["reaction_and_decision"]] <- "Visual reaction and decision"

data %<>% 
  mutate(label = sapply(type, function(t) type_id[[t]])) %>% 
  mutate(type = factor(type, levels = c("reaction_visual", "reaction_auditory", "reaction_and_decision")))
```


## Data visualization

```{r message=FALSE}
data %>%
  filter(type %in% c("reaction_visual", "reaction_and_decision")) %>%
  ggplot(aes(x=score, fill=type)) +
  geom_density(alpha=0.6, outline.type = "lower") +
  scale_fill_discrete(labels=data$label) +
  labs(title="Distribution of response times for simple visual reaction vs. deciding based on colour", x="Time to respond (s)") +
  xlim(0.05, 2 / 3) +
  theme_minimal()
```

>For the simple **reaction only**-condition, we see a lot of *positive kurtosis*, while for the **react and decide**-condition we see a great amount of *negative kurtosis* as well as a tiny bit of *positive skewness*.

## Reaction time for visual- vs auditory stimuli

```{r}
data %>%
  filter(type %in% c("reaction_visual", "reaction_auditory")) %>%
  ggplot(aes(x=score, fill=type)) +
  geom_density(alpha=0.6, outline.type = "lower") +
  scale_fill_discrete(labels=data$label) +
  labs(title="Distribution of response times for visual- and auditory stimuli", x="Time to respond (s)") +
  xlim(0.05, 2 / 3) +
  theme_minimal()
```

## Over time

```{r message=FALSE}
data %>%
  ggplot(aes(x=hour(date), y=log10(score), color=type)) +
  geom_boxplot() +
  labs(title="Development of results across time", x = "Time", y="Time to respond (s)") +
  theme_minimal()
```

